Initial Analysis

### 2019-11-28 Initial_Analysis.Rmd
Fixed the last name issues with the map

### Non-transboundary Tresh 1
# Clean_Non_Transboundary_Data <- Non_Transboundary_Data %>% 
#   rename(eez_name = Territory) %>% 
#   left_join(sau_eez_fes) %>% 
#   group_by(Territory = fishing_entity) %>% 
#   summarise(value = length(unique(TaxonKey)),
#             Taxons = paste(unique(TaxonKey),collapse = ";"))

## Determine as Trans. those species that are both trans and discrete for a nation (Tresh 2 and 3)
# Tresholded_D_Data <- Clean_Results_Trans %>% 
#   filter(Model_Index == MI) %>% 
#   mutate(Species_Type = ifelse(Area_Index > Max_AI,"Discrete",
#                                ifelse(Area_Index < Min_AI,NA,
#                                       "Transboundary"))
#   ) %>% 
#   filter(!is.na(Species_Type)) %>% 
#   group_by(CT_fishing_entity,Species_Type,TaxonKey) %>%
#   summarise(n=n()) %>%
#   spread(Species_Type,n) %>% 
#   mutate(Discrete = ifelse(!is.na(Discrete) & !is.na(Transboundary),NA,Discrete)) %>% 
#   gather("Species_Type","value", Discrete:Transboundary) %>% 
#   filter(!is.na(value),
#          Species_Type == "Discrete") %>% 
#   group_by(Territory = CT_fishing_entity) %>% 
#   summarise(value = length(unique(TaxonKey)),
#             Taxons = paste(unique(TaxonKey),collapse = ";")) %>% 
#   #  Include discrete species of Trsh. 1
#   bind_rows(Clean_Non_Transboundary_Data) %>%
#   # Data cleaning (group by territory and include georegions for plot)
#   rename(FishingRegion=Territory) %>% 
#   left_join(Clean_sau_eez_fes) %>% 
#   group_by(Territory = fishing_entity)

@@

Revenue_Country <- sau_eez_fes %>% 
  group_by(fishing_entity_id, fishing_entity) %>% 
  summarise(n=n()) %>% 
  select(-n) %>% 
  full_join(Tresholded_T_Data,
            by = "fishing_entity") %>% 
  group_by(fishing_entity_id,
           fishing_entity,
           taxon_key) %>% 
  summarise(n()) %>% 
  left_join(SAU_Revenue_Data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  group_by(fishing_entity) %>% 
  summarise(Total_USD = (sum(mean_value,na.rm=T))/1000000) %>% # Million of USD
  mutate(fishing_entity = ifelse(fishing_entity == "USA","United States of America",fishing_entity),
         Bins = cut(Total_USD,breaks = 4),
         Bins_Plot = cut(Total_USD,breaks = 4,
                         labels = c('super low', 'low','high','super high'))
  ) %>% 
  filter(Total_USD > 0)

@@

save_plot("Plot2.png",
          plot,
          base_height = 8,
          base_width = 13)

Plot_Name <- paste("New_100_25_Bins_Value.png", sep = "")

@@

>>>>

@@

Revenue_Country <- sau_eez_fes %>% 
  group_by(fishing_entity_id, fishing_entity) %>% 
  summarise(n=n()) %>% # Get all of the fishing entity and id
  select(-n) %>% 
  full_join(Tresholded_T_Data,
            by = "fishing_entity") %>% 
  group_by(fishing_entity_id,
           fishing_entity,
           taxon_key) %>% 
  summarise(n()) %>% # get each taxa per nation
  left_join(SAU_Revenue_Data,
            by = c("fishing_entity_id","taxon_key")) %>% 
  group_by(fishing_entity) %>% # Estimate the amount of dollars of each nation 
  summarise(Total_USD = (sum(mean_value,na.rm=T))/1000000) %>% # Million of USD
  mutate(fishing_entity = ifelse(fishing_entity == "USA","United States of America",
                                 ifelse(fishing_entity == "Russian Federation","Russia",fishing_entity)),
         Bins = cut(Total_USD,breaks = 4),
         Bins_Plot = cut(Total_USD,breaks = 4,
                         labels = c('super low', 'low','high','super high'))
  ) %>% 
  filter(Total_USD > 0)

@@

Plot_Name <- paste("100_25_Bins_Value_Region.png", sep = "")

save_plot(Plot_Name,
          plot,
          base_height = 8,
          base_width = 13)

@@

### Fixing Russia Moneeeeey

```{r russia}

# Shapefile names
Russia_Sf <- World_land_sf %>% 
  filter(str_detect(fishing_entity,"Russia")) %>% 
  pull(fishing_entity)

"Russia"

Russia_Trans <- Revenue_Country %>% 
  filter(str_detect(fishing_entity,"Russia")) %>% 
  pull(fishing_entity)

"Russian Federation"
### Laptev and Chukchi are the issue, No Alaska'?

### Wake
Wake_ssf <- World_sf %>% 
  filter(str_detect(eez_name,"Wake")) %>% 
  pull(eez_name)

"Wake Isl. (USA)"

Wake_Trans <- Transboundary_Spp %>% 
  filter(str_detect(eez_name,"Wake")) %>% 
  pull(eez_name)

"NA"

Wake_Tresh <- Tresholded_T_Data %>% 
  filter(str_detect(eez_name,"Wake")) %>% 
  pull(eez_name)

"NA"

Wake_Raw <- Clean_Results_Trans %>% 
  filter(str_detect(eez_name,"Wake"))

#### Son todas under 25%.... Por eso

#### Macquarie Island
Macquarie_Raw <- Clean_Results_Trans %>% 
  filter(str_detect(eez_name,"Macquarie"))

# Under 25% Bye

### Minomi

Neighbours_Data %>% 
  filter(str_detect(Territory,"Japan")) %>% 
  pull(Territory) %>% 
  unique()

# Not in our shaopefile
